### 2019-11-26 ic-journal/context.tex
Removed all reviewed highlights in the first part of the paper; re-enable highlights
Cumulative fixes with highlights
It is recommended that "cf." be used only to suggest a comparison, and the word "see" be used to point to a source of information.
https://en.wikipedia.org/wiki/List_of_Latin_abbreviations

We have chosen to use $\lambda$-expressions (with the type
``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
to represent \emph{multi-hole contexts}.
%
This choice has a significant advantage over \emph{one-hole
contexts}, as each hole corresponds to one
appearance of the \emph{same} variable in single-variable
expressions (or equations). Thus \emph{contexts} can be directly used in
formulating the unique solution of equations theorems in
single-variable cases. The precise definition is given inductively:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}. \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}. \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[CONTEXT_rules]}
\end{alltt}
Notice in above inductive definitions, for any CCS term $p$,
\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}} is a valid context. In this case there is no
hole in the context. On the other hand, if any CCS term with recursion
could be a context, the recursion must be a subterm of this $p$.

A context is \emph{weakly guarded} (\texttt{WG}) if each hole is
underneath a prefix:
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}. \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}. \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[WG_rules]}
\end{alltt}
(Notice the differences between a weak guarded context and a normal
one: $\lambda t. t$ is not weakly guarded as the variable is directly
exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)

A context is \emph{guarded} (\texttt{SG}) if each hole is underneath a \emph{visible} prefix:
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{label} \HOLBoundVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}. \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}. \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[SG_rules]}
\end{alltt}

A context is \emph{sequential} (\texttt{SEQ}) if each of its \emph{subcontexts} with
a hole, apart from the hole itself, is in forms of prefixes or sums:
(c.f. Def.~\ref{def:guardness} and p.101,157 of \cite{Mil89} for
the informal definitions.)
 \begin{alltt}
\HOLTokenTurnstile{} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{SEQ} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}. \HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{e\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\hfill{[SEQ_rules]}
\end{alltt}

@@

   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a\sb{\mathrm{1}}} \HOLBoundVar{a\sb{\mathrm{2}}} \HOLBoundVar{e\sb{\mathrm{1}}} \HOLBoundVar{e\sb{\mathrm{2}}}.

>>>>

We have chosen to use $\lambda$-expressions (with the type
``\HOLinline{\ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS} \HOLTokenTransEnd \ensuremath{(}\ensuremath{\alpha}, \ensuremath{\beta}\ensuremath{)} \HOLTyOp{CCS}}'')
to represent \emph{multi-hole contexts}.
%
This choice has a significant advantage over \emph{one-hole
contexts}, as each hole corresponds to one
appearance of the \emph{same} variable in single-variable
expressions (or equations). Thus \emph{contexts} can be directly used in
formulating the unique solution of equations theorems in
single-variable cases. The precise definition is given inductively:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[CONTEXT_rules]}
\end{alltt}
Notice in above inductive definitions, for any CCS term $p$,
\HOLinline{\HOLTokenLambda{}\HOLBoundVar{t}.\\\;\HOLFreeVar{p}} is a valid context. In this case there is no
hole in the context. On the other hand, if any CCS term with recursion
could be a context, the recursion must be a subterm of this $p$.

A context is \emph{weakly guarded} (\texttt{WG}) if each hole is
underneath a prefix:
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{WG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{WG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[WG_rules]}
\end{alltt}
(Notice the differences between a weak guarded context and a normal
one: $\lambda t. t$ is not weakly guarded as the variable is directly
exposed without any prefixed action. And $\lambda t. a.e[t]$ is weakly
guarded as long as $e[\cdot]$ is a context, not necessary weakly guarded.)

A context is \emph{guarded} (\texttt{SG}) if each hole is underneath a \emph{visible} prefix:
\begin{alltt}
\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{l} \HOLBoundVar{e}. \HOLConst{CONTEXT} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{label} \HOLBoundVar{l}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SG} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{\mid}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{L} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{(\nu}\HOLBoundVar{L}\ensuremath{)} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{rf} \HOLBoundVar{e}. \HOLConst{SG} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLConst{relab} \ensuremath{(}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)}\hfill{[SG_rules]}
\end{alltt}

A context is \emph{sequential} (\texttt{SEQ}) if each of its \emph{subcontexts} with
a hole, apart from the hole itself, is in forms of prefixes or sums:
(See Def.~\ref{def:guardness} and \citep[p.~101, 157]{Mil89} for
the informal definitions.)
 \begin{alltt}
\HOLTokenTurnstile{} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{t}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{p}. \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{p}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{a} \HOLBoundVar{e}. \HOLConst{SEQ} \HOLBoundVar{e} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \HOLBoundVar{a}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{e} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}. \HOLConst{SEQ} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{SEQ} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{SEQ} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\hfill{[SEQ_rules]}
\end{alltt}

@@

   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}}.
        \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{GCONTEXT} \ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLSymConst{\HOLTokenImp{}} \HOLConst{GCONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{\HOLBoundVar{a}\sb{\mathrm{1}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{1}}} \HOLBoundVar{t} \HOLSymConst{\ensuremath{+}} \ensuremath{\HOLBoundVar{a}\sb{\mathrm{2}}}\HOLSymConst{\ensuremath{\ldotp}}\ensuremath{\HOLBoundVar{e}\sb{\mathrm{2}}} \HOLBoundVar{t}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
